Making sure the variances converge with 3 circles

### 2024-07-22 Two_var3.Rmd
Finition

```{r}
cat("Monte Carlo variance:", res1_nb)
# Examples:
# Monte Carlo variance: 2717279
```

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Examples:
# Mean of the variance of bootstrap samples: 2684541
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Examples:
# We get a difference of: 1.21952%
```

>>>>

```{r}
cat("Monte Carlo variance:", res1_nb)
# Example:
# Monte Carlo variance: 2717279
```

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res2_nb)
# Example:
# Mean of the variance of bootstrap samples: 2684541
```

```{r}
cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
# Example:
# We get a difference of: 1.21952%
```
